Parallel Global Optimization for Non-Convex Mixed-Integer Problems \thanks{This study was supported by the Russian Science Foundation, project No.\,16-11-10150.}

### 2019-04-11 2019/RSD_Integer/RSD2019.tex
Corrected

In the present paper, the mixed-integer global optimization problems are considered. A novel 
parallel algorithm for solving the problems of this class based on the information-statistical 
approach to solving the continuous global optimization problems has been proposed. 
The comparison of this algorithm with known analogs demonstrating the efficiency of the 
developed approach has been conducted. 
%Russian
The proposed algorithm allows an efficient parallelization including the employment of the 
graphics accelerators. 
The results of performed numerical experiments (solving a series of 100 multiextremal mixed-
integer problems) confirm a good speed-up of the algorithm with the use of GPU.

@@

In the present paper, the global optimization problems and the method of solving these ones are 
considered. The global optimization problems are the computation-costly ones since the global 
optimum is an integral characteristic of the problem being solved and requires the investigation 
of the whole search domain. 
As a result, the search of the global optimum is reduced to the construction of a coverage (in 
general, a nonuniform one) of the space of parameters. 
The problems, in which some parameters can take the integer values only (mixed-integer global 
optimization problems) are of special interest because for these ones it is more difficult to build 
the estimates of the optimum as compared to the continuous problems.

@@

A lot of publication have been devoted to the methods of solving the mixed-integer problems 
(see, for example, the reviews~\cite{Burer,Boukouvala}). The well known deterministic 
methods of solving the problems of this class are based, as a rule, on the Branch-and-Bound 
approach \cite{Belotti} or on the Branch-and-Reduce one \cite{Vigerske}. Also, a number of 
the metaheuristic and genetic 
algorithms are known, which are based one way or another on the random search concept 
\cite{Deep,Schluter}.

In the present study, we proposed a novel parallel method for solving the mixed-integer 
problems based on the information-statistical approach to solving the global optimization 
problems \cite{Strongin2000,Strongin2013}. 
%Russian
Within the framework of this approach: 
\begin{itemize}
	\item 
	the solving of the multidimensional problems is reduced to solving the equivalent one-
dimensional problems; the corresponding reduction is based on the use of the space-filling 
curves;
	\item 
	when solving the constrained optimization problems, each constraint is taken into 
account and processed separately, the penalty functions are not used;
	\item 
	the parallelization of the search process is performed by means of the simultaneous 
computing of several objective function values at different points of the search domain within 
every iteration.
\end{itemize}

The paper text reflecting the results of the performed study is organized in the following way. 
In Section 2, a brief description of the dimensionality reduction scheme using the space-filling 
curves is given. Also, the index scheme of accounting for the constraints is described. Here the 
formulation of the parallel index algorithm for solving the continuous global optimization 
problems is given as well.
In Section 3, the approach to the generalization of the parallel index algorithm with the purpose 
of solving the mixed-integer problems is presented. A method allowing reducing the solving of 
mixed-integer problem to solving a set of the continuous optimization problems, which can be 
performed in parallel, is given. 
Section 4 contains the results of numerical experiments. The comparison of the sequential 
version of the algorithm with the known analogs is conducted here. Also, the efficiency of the 
parallel CPU- and GPU-versions of the algorithm for solving a series of the multiextremal 
mixed-integer problem is demonstrated. 
Section 5 concludes the paper.

@@

By employing the continuous single-valued Peano-Hilbert curve $y(x)$ mapping the unit 
interval 
$[0,1]$ on the $x$-axis onto the $N$-dimensional domain (\ref{D}), it is possible to find the 
minimum in (\ref{problem}) by solving the one-dimensional problem
\[
\varphi(y(x^\ast))=\min \left\{\varphi(y(x)): x \in [0,1], \; g_i(y(x))\leq 0, \; 1 \leq i \leq m\right\}.
\]
Algorithms for numerical construction of Hilbert curve approximation (\textit{evolvent}) are 
considered in \cite{Strongin2013}. These evolvents are fractals generated by an iterative
process, that fill in the hypercube $D$ with accuracy $2^{-m}$, where integer $m>0$ is the 
evolvent construction parameter.

Problems of numerical construction of Peano-type space filling curves and the corresponding 
theory are considered in detail in \cite{Strongin2000,Strongin2013}. Examples of the evolvent 
with different $m$ in two dimensions are given in Fig.~\ref{evolvents}.

@@

Suppose we have $p \geq 1$  computational elements (e.g., accelerator cores), which can be 
used to run $p$ trials simultaneously. In the first iteration of the method, $p$ trials are run in 
parallel at various random points $x^i\in(0,1)$, $1\leq i \leq p$. 
Suppose $n \geq 1$  iterations of the method have been completed, and as a result of which, 
trials were carried out in $k=k(n)$ points $x^i, 1\leq i \leq k$. Then the points 
$x^{k+1},...,x^{k+p}$  of the search trials in the next $(n+1)$-th iteration will be determined 
according to the rules below.

\begin{enumerate}
\item 
Renumber the points $x^1,...,x^k$ from previous iterations with lower indices, lowest to highest 
coordinate values, i.e.
\begin{equation}\label{Eq:17}
0=x_0<x_1<...<x_i<...<x_k<x_{k+1}=1,
\end{equation}
and match them with the values $z_i=g_\nu(y(x_i))$, $\nu=\nu(x_i)$, $1 \leq i \leq k$, from 
(\ref{trial_result}), calculated at these points; points $x_0=0$ and $x_{k+1}=1$ are introduced 
additionally; the values $z_0$ and $z_{k+1}$ are indeterminate.
\item
Classify the numbers $i,1\leq i \leq k$, of the trial points from (\ref{Eq:17}) by the number of 
problem constraints fulfilled at these points, by building the sets
\begin{equation}\label{Eq:18}
I_\nu = \left\{i: 1 \leq i \leq k,\ \nu = \nu(x_i)\right\},\ 1 \leq \nu \leq m+1,
\end{equation}
containing the numbers of all points $x_i,1\leq i \leq k$, with the same values of $\nu$. The end 
points $x_0=0$ and $x_{k+1}=1$ are interpreted as those with zero indices, and they are 
matched to an additional set $I_0={0,k+1}$.

Identify the maximum current value of the index
\begin{equation}\label{Eq:19}
M=\max \left\{\nu = \nu(x_i), \ 1\leq i \leq k\right\}.
\end{equation}
\item
For all values of $\nu, \ 1\leq \nu \leq m+1$, calculate the values  
\begin{equation}\label{Eq:20}
\mu_\nu = \max \left\{ \frac{\left|z_i-z_j\right|}{\left(x_i-x_j\right)^{1/N}} : i,j \in I_\nu, 
j<i\right\}.
\end{equation}
If the set $I_\nu$ contains less than two elements or $\mu_\nu$ from (\ref{Eq:20}) equals zero, 
then assume $\mu_\nu=1$.
\item
For all non-empty sets $I_\nu$, $1 \leq \nu \leq m+1$, determine the values
\begin{equation}\label{Eq:21}
  z^\ast_\nu =  
   \begin{cases}
    -\epsilon_\nu,  \nu < M, \\
    \min{\left\{g_\nu(x_i):i\in I_\nu\right\}}, \nu = M,
   \end{cases}
\end{equation}
where $M$ is the maximum current value of the index, and the vector
\begin{equation}\label{Eq:22}
\epsilon _R=\left(\epsilon_1,...,\epsilon_m\right),
\end{equation}
with positive coordinates is called the \textit{reserve vector} and is used as a parameter in the 
algorithm.
\item
For each interval $(x_{i-1},x_i)$,$1 \leq i \leq k+1$, calculate the \textit{characteristic} $R(i)$: 
\[
R(i)=\Delta_i+ \frac{(z_i-z_{i-1})^2}{(r_\nu\mu_\nu)^2\Delta_i}-2\frac{z_i+z_{i-1}-
2z^\ast_\nu}{r_\nu\mu_\nu},\;\; \nu=\nu(x_{i-1})=\nu(x_i),
\]
\[
R(i)= 2\Delta_i-4\frac{z_i-z^\ast_\nu}{r_\nu\mu_\nu},\;\; \nu(x_{i-1})<\nu(x_i)=\nu,
\]
\[
R(i)= 2\Delta_i-4\frac{z_{i-1}-z^\ast_\nu}{r_\nu\mu_\nu},\;\; \nu = \nu(x_{i-1})>\nu(x_i).
\]
where $\Delta_i=(x_i-x_{i-1})^{1/N}$, and the values $r_\nu>1, 1\leq\nu\leq m+1$, are used as 
parameters in the algorithm.
\item
Reorder the characteristics $R(i)$, $1\leq i \leq k+1$, from highest to lowest 	
\begin{equation}\label{Eq:23}
R(t_1)\geq R(t_2)\geq ... \geq R(t_{k})\geq R(t_{k+1})
\end{equation}
and choose $p$ largest characteristics with interval numbers $t_j, 1\leq j \leq p$.
\item
Carry out $p$ new trials in parallel at the points $x^{k+j}, 1 \leq j \leq p$, calculated by the 
formulae
\begin{eqnarray*}
& x^{k+j}=\frac{x_{t_j}+x_{t_j-1}}{2}, \; \nu(x_{t_j-1})\neq \nu(x_{t_j}), \\
& x^{k+j}=\frac{x_{t_j}+x_{t_j-1}}{2}- \frac{\mathrm{sign}(z_{t_j}-z_{t_j-
1})}{2r_\nu}\left[\frac{\left|z_{t_j}-z_{t_j-1}\right|}{\mu_\nu}\right]^N, \; \nu(x_{t_j-
1})=\nu(x_{t_j})=\nu. \\
\end{eqnarray*}

@@

The algorithm stops if the condition $\Delta_{t_j}\leq \epsilon$ becomes true for at least one 
number $t_j, 1\leq j \leq p$; here  $\epsilon>0$ has an order of magnitude of the desired 
coordinate accuracy.
A detailed description of the algorithm convergence theory is presented in \cite{Strongin2000}.

@@

Let us number by the integer values $s, 1\leq s \leq S,$ all possible values of the vector $u$, i.e. 
juxtapose each considered value $s$ with the vector $u_s$. 
Then, the considered problem can be written in the form 
\begin{gather}\label{problem_is}
 \min_{s\in\{1,...,S\}}\left(\min{\left\{ g_{m+1}(y,u_s):y\in D, \; g_i(y,u_s)\leq 0, \; 1 \leq i \leq 
m\right\}}\right),\\
D=\left\{ a_j\leq y_j \leq b_j, \; 1 \leq j\leq N \right\}.\nonumber 
\end{gather}

@@

As an illustration, Fig. \ref{fig:1} presents the plots of the functions corresponding to a 
problem 
\[
%\min{\left\{ x^2 - 10\cos(2\pi x) + u^2 - 10\cos(2\pi u) : x\in [-2.22, 1.8], u \in {0,1} \right\}}
\min{\left\{ u^2 (\sin(x) +\sin(10x/3) : x\in [2.7, 7.5], u \in {1,2} \right\}}
\]
with one continuous parameter $x$ and one binary parameter $u$.
%Еще один график?

@@

\begin{table}
	\caption{Comparison of MIPIA and GA}
	\label{tab:1}
	\center
	\begin{tabular}{cccccc}
		\hline\noalign{\smallskip}
	\multirow{2}{*}{Test problem}	 & \multicolumn{2}{c}{ GA } & & 
\multicolumn{2}{c}{MIGSA} \\
		\noalign{\smallskip} \cline{2-3} \cline{5-6} \noalign{\smallskip}
		 & $k$ & $t$ & & $k$ & $t$  \\
		\noalign{\smallskip} \hline \noalign{\smallskip}
		 Problem 2 \cite{Floudas}&	481 &	0.0601 & &	417 &	0.04 \\
		 Problem 3 \cite{Floudas}& 	1821 &	0.1130 & & 3324 &	0.107 \\
		 Problem 6 \cite{Floudas}&	641 &	0.0510 & &	118 &	0.001 \\
		 Problem 1 \cite{Deep}   &	481 &	0.1378 & &	66 &	0.0007 \\
		 Problem 2 \cite{Deep}   &	481 &	0.0473 & &	57 &	0.0006 \\
		 Problem 7 \cite{Deep}   &	841 &	0.0736 & & 372	 &	0.017 \\
		\noalign{\smallskip}\hline
	\end{tabular}
\end{table}

@@

\begin{enumerate}
	\item A continuous multiextremal function $\varphi(y), y\in D = \left\{ a_j\leq 
y_j\leq b_j, 1\leq j \leq N \right\}$ is generated with the use of the GKLS generator. The global 
minimum of this function is achieved at the known point $y'=(y'_1,...,y'_N)$ and equals 
$\varphi'=\varphi(y')=-1$.
	\item A concave mixed-integer function 
	\[
			\mu(y,u) = -2 \left[ \sum_{j=1}^N \left( \frac{y_j - y'_j}{b_j-a_j} 
\right)^2 + \sum_{j=1}^M \left( \frac{u_j - b_j}{b_j-a_j} \right)^2 \right],
	\]
	is generated where 
	\begin{gather}
	y\in D = \left\{ a_j\leq y_j\leq b_j, 1\leq j \leq N \right\} \subset R^N,\nonumber \\
	u\in U = \left\{ u_j \in  \left\{a_j, ..., b_j \right\}, 1\leq j \leq M \right\}.\nonumber
	\end{gather}
	This function has $N$ continuous and $M$ discrete parameters and achieves its 
minimum value at the point $(y',b)$.
	\item The coefficient 
	\[
	C = 4 - \min_{y,u} \left\{ \mu(y,u) \right\}, \; y\in D, u \in U.
	\]
	is computed. 
It is obvious, that the minimum of a concave function $\mu(y,u)$ is located at one of the corner 
points of the search domain. Therefore, if the problem dimensionality is of the order of 10 it can 
be found by the brute force method.
	\item A multiextremal mixed-integer function 
	\[
	f(y,u) = \left(\varphi(y) + \sum_{j=1}^M{u_j}\right)\left(C + \mu(y,u)\right).
	\]
	is formed.
By construction, $f(y,u)$ would take its minimum value at the point $(y',b)$.

@@

A hundred 11-dimensional mixed-integer problems of this type were generated in total. 
For the purpose of simulation of the computational complexity inherent to
applied problems of optimization, calculation of the objective function in all performed
experiments was made more complex by additional calculations without changing the type
of function and arrangement of its minima (series summation from 80 thousand elements).
The accuracy of the search was equal to $10^{-2}$.%Параметры метода!!!

@@

\section{Conclusion}
%Russian
In the present paper, the results obtained in Lobachevskii State University of Nizhni Novgorod 
when developing and investigating the parallel global optimization algorithms for solving the 
multiextremal problems, in which some parameters are continuous and the others are the discrete 
ones are presented. 
An efficient parallel algorithm has been proposed for solving the problems of the specified class. 
In the sequential variant, this algorithm does not inferior to similar purpose algorithm 
implemented in Matlab Global Optimization Toolbox.
In the parallel variant, the proposed algorithm allows the efficient implementations on CPU as 
well as on GPU. 
The numerical experiments on a series of 100 multiextremal mixed-integer test problems have been carried out 
convincingly demonstrating a good speedup of the algorithm with the use of GPU.
Thus, the parallel algorithm with the use of GPU demonstrated the time speedup $S = 182$ 
relative to the sequential one and $S = 23.7$ relative to the algorithm fully employing two CPU on 
the cluster node.

>>>>

The paper considers the mixed-integer global optimization problems. A novel 
parallel algorithm for solving the problems of this class based on the index 
algorithm to solving the continuous global optimization problems has been proposed. 
The comparison of this algorithm with known analogs demonstrates the efficiency of the 
developed approach. 
%Russian
The proposed algorithm allows an efficient parallelization including the employment of the 
graphics accelerators. The results of performed numerical experiments (solving a series of 100 multiextremal mixed-integer problems) confirm a good speedup of the algorithm with the use of GPU.

@@

In this paper the global optimization problems and the method of solving these ones are 
considered. The global optimization problems are the time-consuming ones since the global 
optimum is an integral characteristic of the problem being solved and requires the investigation 
of the whole search domain. 
As a result, the search of the global optimum is reduced to the construction of a coverage (in 
general, a nonuniform one) of the space of parameters. 
The problems, in which some parameters can take the discrete or integer values only (mixed-integer global 
optimization problems) are of special interest because for these problems it is more difficult to build 
the estimates of the optimum as compared to the continuous ones.

@@

A lot of publication have been devoted to the methods of solving the mixed-integer problems 
(see, for example, the reviews~\cite{Burer,Boukouvala}). The well known deterministic 
methods of solving the problems of this class are based, as a rule, on the Branch-and-Bound 
\cite{Belotti} or on the Branch-and-Reduce approach \cite{Vigerske}. Also, a number of 
the metaheuristic and genetic 
algorithms are known, which are based one way or another on the random search concept 
\cite{Deep,Schluter}.

In the present study, we proposed a novel parallel method for solving the mixed-integer 
problems based on the index approach to solving the constrained global optimization 
problems \cite{Strongin2000,Strongin2013}. 
%Russian
Within the framework of this approach: 
\begin{itemize}
	\item 
	the solving of the multidimensional problems is reduced to solving the equivalent one-dimensional problems; the corresponding reduction is based on the use of the space-filling curves;
	\item 
	when solving the constrained optimization problems, each constraint is taken into 
account and processed separately, the penalty functions are not used;
	\item 
	the parallelization of the search process is performed by means of the simultaneous 
computing of several objective function values at different points of the search domain within 
every iteration.
\end{itemize}

The paper text reflecting the results of the performed study is organized in the following way. 
In Section 2, a brief description of the dimensionality reduction scheme using the space-filling 
curves is given. Also, the index scheme of accounting for the constraints is described. Here the 
formulation of the parallel index algorithm for solving the continuous global optimization 
problems is given as well.
In Section 3, the approach to the generalization of the parallel index algorithm with the purpose 
of solving the mixed-integer problems is presented. A method that allows to reduce solving of 
mixed-integer problem to solving a set of the continuous optimization problems, which can be 
performed in parallel, is given. 
Section 4 contains the results of numerical experiments. The comparison of the sequential 
version of the algorithm with the known analogs is conducted here. Also, the efficiency of the 
parallel CPU- and GPU-versions of the algorithm for solving a series of the multiextremal 
mixed-integer problem is demonstrated. 
Section 5 concludes the paper.

@@

By employing the continuous single-valued Peano-Hilbert curve $y(x)$ mapping the unit 
interval 
$[0,1]$ on the $x$-axis onto the $N$-dimensional domain (\ref{D}), it is possible to find the 
minimum in (\ref{problem}) by solving the one-dimensional problem
\[
\varphi(y(x^\ast))=\min \left\{\varphi(y(x)): x \in [0,1], \; g_i(y(x))\leq 0, \; 1 \leq i \leq m\right\}.
\]
Algorithms for numerical construction of Peano-Hilbert curve approximation (\textit{evolvent}) are 
considered in \cite{Strongin2000,Strongin2013}. These evolvents are fractals generated by an iterative
process, that fill in the hypercube $D$ with accuracy $2^{-m}$, where integer $m>0$ is the 
evolvent construction parameter. Examples of the evolvent with different $m$ in two dimensions are given in Fig.~\ref{evolvents}.

@@

Suppose we have $p \geq 1$  computational elements (e.g., processor cores), which can be 
used to run $p$ trials simultaneously. In the first iteration of the method, $p$ trials are run in 
parallel at various random points $x^i\in(0,1)$, $1\leq i \leq p$. 
Suppose $n \geq 1$  iterations of the method have been completed, and as a result of which, 
trials were carried out in $k=k(n)$ points $x^i, 1\leq i \leq k$. Then the points 
$x^{k+1},...,x^{k+p}$  of the search trials in the next $(n+1)$-th iteration will be determined 
according to the rules below.

\begin{enumerate}
\item 
Renumber the points $x^1,...,x^k$ from previous iterations with lower indices, lowest to highest 
coordinate values, i.e.
\begin{equation}\label{Eq:17}
0=x_0<x_1<...<x_i<...<x_k<x_{k+1}=1,
\end{equation}
and match them with the values $z_i=g_\nu(y(x_i))$, $\nu=\nu(x_i)$, $1 \leq i \leq k$, from 
(\ref{trial_result}), calculated at these points; points $x_0=0$ and $x_{k+1}=1$ are introduced 
additionally, the values $z_0$ and $z_{k+1}$ are indeterminate.
\item
Classify the numbers $i,1\leq i \leq k$, of the trial points from (\ref{Eq:17}) by the number of 
problem constraints fulfilled at these points, by building the sets
\begin{equation}\label{Eq:18}
I_\nu = \left\{i: 1 \leq i \leq k,\ \nu = \nu(x_i)\right\},\ 1 \leq \nu \leq m+1,
\end{equation}
containing the numbers of all points $x_i,1\leq i \leq k$, with the same values of $\nu$. The end 
points $x_0=0$ and $x_{k+1}=1$ are interpreted as those with zero indices, and they are 
matched to an additional set $I_0= \left\{ 0,k+1 \right\}$.

Identify the maximum current value of the index
\begin{equation}\label{Eq:19}
M=\max \left\{\nu = \nu(x_i), \ 1\leq i \leq k\right\}.
\end{equation}
\item
For all values of $\nu, \ 1\leq \nu \leq m+1$, calculate the values  
\begin{equation}\label{Eq:20}
\mu_\nu = \max \left\{ \frac{\left|z_i-z_j\right|}{\left(x_i-x_j\right)^{1/N}} : i,j \in I_\nu, 
j<i\right\}.
\end{equation}
If the set $I_\nu$ contains less than two elements or $\mu_\nu$ from (\ref{Eq:20}) equals zero, 
then assume $\mu_\nu=1$.
\item
For all non-empty sets $I_\nu$, $1 \leq \nu \leq m+1$, determine the values
\begin{equation}\label{Eq:21}
  z^\ast_\nu =  
   \begin{cases}
    -\epsilon_\nu,  \nu < M, \\
    \min{\left\{g_\nu(x_i):i\in I_\nu\right\}}, \nu = M,
   \end{cases}
\end{equation}
where $M$ is the maximum current value of the index, and the vector $\epsilon _R=\left(\epsilon_1,...,\epsilon_m\right)$ with positive coordinates is called the \textit{reserve vector} and is used as a parameter in the 
algorithm.
\item
For each interval $(x_{i-1},x_i)$,$1 \leq i \leq k+1$, calculate the \textit{characteristic} $R(i)$: 
\[
R(i)=\Delta_i+ \frac{(z_i-z_{i-1})^2}{(r_\nu\mu_\nu)^2\Delta_i}-2\frac{z_i+z_{i-1}-
2z^\ast_\nu}{r_\nu\mu_\nu},\;\; \nu=\nu(x_{i-1})=\nu(x_i),
\]
\[
R(i)= 2\Delta_i-4\frac{z_i-z^\ast_\nu}{r_\nu\mu_\nu},\;\; \nu(x_{i-1})<\nu(x_i)=\nu,
\]
\[
R(i)= 2\Delta_i-4\frac{z_{i-1}-z^\ast_\nu}{r_\nu\mu_\nu},\;\; \nu = \nu(x_{i-1})>\nu(x_i).
\]
where $\Delta_i=(x_i-x_{i-1})^{1/N}$, and the values $r_\nu>1, 1\leq\nu\leq m+1$, are used as 
parameters in the algorithm.
\item
Reorder the characteristics $R(i)$, $1\leq i \leq k+1$, from highest to lowest 	
\begin{equation}\label{Eq:23}
R(t_1)\geq R(t_2)\geq ... \geq R(t_{k})\geq R(t_{k+1})
\end{equation}
and choose $p$ largest characteristics with interval numbers $t_j, 1\leq j \leq p$.
\item
Carry out $p$ new trials in parallel at the points $x^{k+j}, 1 \leq j \leq p$, calculated by the 
formulae
\begin{eqnarray*}
& x^{k+j}=\frac{x_{t_j}+x_{t_j-1}}{2}, \; \nu(x_{t_j-1})\neq \nu(x_{t_j}), \\
& x^{k+j}=\frac{x_{t_j}+x_{t_j-1}}{2}- \frac{\mathrm{sign}(z_{t_j}-z_{t_j-
1})}{2r_\nu}\left[\frac{\left|z_{t_j}-z_{t_j-1}\right|}{\mu_\nu}\right]^N, \; \nu(x_{t_j-
1})=\nu(x_{t_j})=\nu. \\
\end{eqnarray*}

@@

The algorithm stops if the condition $\Delta_{t_j}\leq \epsilon$ becomes true for at least one 
number $t_j, 1\leq j \leq p$; here  $\epsilon>0$ has an order of magnitude of the desired 
coordinate accuracy.

This method of organizing parallel computing has the following justification.
The characteristics of intervals $R(i)$ used in the index algorithm can be considered as
probability measures of the global minimum point location in these intervals. Inequalities
(\ref{Eq:23}) arrange intervals according to their characteristics, and trials are carried out in parallel in
the first $p$ intervals with the largest probabilities.
A detailed description of the algorithm convergence theory is presented in \cite{Strongin2000}.

@@

Let us number by the integer values $s, 1\leq s \leq S,$ all possible values of the vector $u$, i.e. 
juxtapose each considered value $s$ with the vector $u_s$. 
Then, the considered problem can be written in the form 
\begin{gather}\label{problem_is}
 \min_{s\in\{1,...,S\}} \left\{ \min_{}{\left\{ g_{m+1}(y,u_s):y\in D, \; g_i(y,u_s)\leq 0, \; 1 \leq i \leq 
m\right\}}\right\},\\
D=\left\{ a_j\leq y_j \leq b_j, \; 1 \leq j\leq N \right\}.\nonumber 
\end{gather}

@@

As an illustration, Fig. \ref{fig:1} presents the plots of the functions corresponding to a 
problem 
\[
%\min{\left\{ x^2 - 10\cos(2\pi x) + u^2 - 10\cos(2\pi u) : x\in [-2.22, 1.8], u \in {0,1} \right\}}
\min{\left\{ u^2 (\sin(x) +\sin(10x/3) : x\in [2.7, 7.5], u \in \{1,2\} \right\}}
\]
with one continuous parameter $x$ and one binary parameter $u$.
%Еще один график?

@@

\begin{table}
	\caption{Comparison of MIPIA and GA}
	\label{tab:1}
	\center
	\begin{tabular}{cccccc}
		\hline\noalign{\smallskip}
	\multirow{2}{*}{Test problem}	 & \multicolumn{2}{c}{ GA } & & 
\multicolumn{2}{c}{MIPIA} \\
		\noalign{\smallskip} \cline{2-3} \cline{5-6} \noalign{\smallskip}
		 & $k$ & $t$ & & $k$ & $t$  \\
		\noalign{\smallskip} \hline \noalign{\smallskip}
		 Problem 2 \cite{Floudas}&	481 &	0.0601 & &	417 &	0.04 \\
		 Problem 3 \cite{Floudas}& 	1821 &	0.1130 & & 3324 &	0.107 \\
		 Problem 6 \cite{Floudas}&	641 &	0.0510 & &	118 &	0.001 \\
		 Problem 1 \cite{Deep}   &	481 &	0.1378 & &	66 &	0.0007 \\
		 Problem 2 \cite{Deep}   &	481 &	0.0473 & &	57 &	0.0006 \\
		 Problem 7 \cite{Deep}   &	841 &	0.0736 & & 372	 &	0.017 \\
		\noalign{\smallskip}\hline
	\end{tabular}
\end{table}

@@

\begin{enumerate}
	\item A continuous multiextremal function $\varphi(y), y\in D = \left\{ a_j\leq 
y_j\leq b_j, 1\leq j \leq N \right\}$ is generated with the use of the GKLS generator. The global 
minimum of this function is achieved at the known point $y'=(y'_1,...,y'_N)$ and equals 
$\varphi(y')=-1$.
	\item A concave mixed-integer function 
	\[
			h(y,u) = -2 \left[ \sum_{j=1}^N \left( \frac{y_j - y'_j}{b_j-a_j} 
\right)^2 + \sum_{j=1}^M \left( \frac{u_j - b_j}{b_j-a_j} \right)^2 \right],
	\]
	is generated where 
	\begin{gather}
	y\in D = \left\{ a_j\leq y_j\leq b_j, 1\leq j \leq N \right\} \subset R^N,\nonumber \\
	u\in U = \left\{ u_j \in  \left\{a_j, ..., b_j \right\}, 1\leq j \leq M \right\}.\nonumber
	\end{gather}
	This function has $N$ continuous and $M$ discrete parameters and achieves its 
minimum value at the point $(y',b)$.
	\item The coefficient 
	\[
	h_{min} = 4 - \min_{y,u} \left\{ h(y,u) \right\}, \; y\in D, u \in U.
	\]
	is computed. 
It is obvious, that the minimum of a concave function $\mu(y,u)$ is located at one of the corner 
points of the search domain. Therefore, if the problem dimensionality is of the order of 10 it can 
be found by the brute force method.
	\item A multiextremal mixed-integer function 
	\[
	f(y,u) = \left(\varphi(y) + \sum_{j=1}^M{u_j}\right)\left(h_{min} + h(y,u)\right).
	\]
	is formed.
By construction, $f(y,u)$ would take its minimum value at the point $(y',b)$.

@@

A hundred 11-dimensional mixed-integer problems of this type were generated in total. 
For the purpose of simulation of the computational complexity inherent to
applied optimization problems, calculation of the objective function in all performed
experiments was made more complex by additional calculations without changing the type
of function and arrangement of its minima (series summation from 80 thousand elements).
The accuracy of the search was equal to $10^{-2}$.%Параметры метода!!!

@@

\section{Conclusion}
%Russian
In the paper the results obtained in Lobachevsky State University of Nizhni Novgorod 
when developing and investigating the parallel global optimization algorithms for solving the 
multiextremal problems, in which some parameters are continuous and the others are the discrete 
ones are presented. 
An efficient parallel algorithm has been proposed for solving the problems of the specified class. 
In the sequential variant, this algorithm does not inferior to similar purpose algorithm 
implemented in Matlab Global Optimization Toolbox.
In the parallel variant, the proposed algorithm allows the efficient implementations on CPU as 
well as on GPU. 
The numerical experiments on a series of 100 multiextremal mixed-integer test problems have been carried out 
convincingly demonstrating a good speedup of the algorithm with the use of GPU.
Thus, the parallel algorithm with the use of GPU demonstrated the time speedup $S = 182$ 
relative to the sequential one and $S = 23.7$ relative to the algorithm fully employing two CPU on 
the cluster node.
